\normalfont \normalsize \textsc{Exoplanet Patchy Cloud Project} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Systematic Error Correction\\ \horrule{2pt} \\[0.5cm]

### 2015-02-11 summary/Systematics1/Systematics1.tex
working result at daniel's office

\subsection{Cosmic Rays in Up-the-Ramp Fitting}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

  \subsection{Cosmic Rays in Up-the-Ramp Fitting}
  \begin{itemize}
  \item In majority of \texttt{ima} files, there are several pixels in
    companion image region that are flagged with 8192 (CR detected by
    up-the-ramp fitting)
    \item it is not clear yet number of pixels that have CR flag is
      correlated with flux scattering
    \item considering use the same PSF images for PSF subtraction.
    \end{itemize}

    \subsection{Jitter}
    \begin{itemize}
    \item 4 exposures have extremely large jitter value
     \item RMS jitter values are about 0.001 arcsec (0.1 pixel)in both
       axes
     \item jitter values seem not to correlate with flux scattering
    \end{itemize}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
